Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-08-14 papers/integration/omm_integ.tex

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{James {et~al.}}
\def\Authors{Sebastian James\,$^{1,2,*}$, Alexander Blenkinsop\,$^{1,2}$, \\
  Alexander Cope\,$^3$, Sean Anderson\,$^{2,4}$, Dimitrios Stanev\,$^5$, \\
  Chris Papapavlou\,$^5$, Konstantinos Moustakas\,$^5$, Kevin Gurney\,$^{1,2}$}
% Affiliations should be keyed to the author's name with superscript
% numbers and be listed as follows: Laboratory, Institute, Department,
% Organization, City, State abbreviation (USA, Canada, Australia), and
% Country (without detailed address information such as city zip codes
% or street names).
%
% If one of the authors has a change of address, list the new address
% below the correspondence details using a superscript symbol and use
% the same symbol to indicate the author in the author list.
\def\Address{\\
$^{1}$Adaptive Behaviour Research Group, Department of Psychology,
  The University of Sheffield, Sheffield, UK \\
$^{2}$Insigneo Institute for in-silico Medicine,
  The University of Sheffield, Sheffield, UK \\
$^{3}$Department of Computer Science,
  The University of Sheffield, Sheffield, UK \\
$^{4}$Department of Automatic Control Systems Engineering,
  The University of Sheffield, Sheffield, UK \\
$^{5}$Department of Computer Science,
  The University of Patras, Patras, Greece \\
}
% The Corresponding Author should be marked with an asterisk. Provide
% the exact contact address (this time including street name and city
% zip code) and email of the corresponding author
\def\corrAuthor{Kevin Gurney}
\def\corrAddress{Department of Psychology, The University of Sheffield,
  Western Bank, Sheffield, S10 2TP, UK}
\def\corrEmail{k.gurney@sheffield.ac.uk}

@@

In addition to the brain model components, all of which are
code-generated using \stob~as described above, three hand-written
components are integrated into the model: The biomechanical eye model;
a component which computes the centroid of a neural layer; and a sensory input
component. The sensory input component takes the eye's rotational state and the
state of the experimental luminances as its inputs and projects a retinotopic
activity map into the brain model. Each of these three BRAHMS
components was hand written in C++. To incorporate these components
into the SpineML model, a model-specific modification was
applied in \stob~(\mycite{cope_spineml_2_brahms_2015}) making use of a \stob~feature designed for this purpose (The external.xsl file).

%\footnote{See the \branch{NoTremor\_Oculomotor\_201603} branch of \url{https://github.com/SpineML/SpineML\_2\_BRAHMS/}}.

Figure \ref{fig:model_framework} shows the workflow, in which the model
specification files (blue box), a combination of SpineML files and C++
code, are processed (green box) into a BRAHMS system (red box).

@@

With the exceptions of the World and
FEF\_add\_noise populations, each neural element represents an
activation whose dynamics depend on the component definition. In the
brain model, there are six different components in use; LINlinear,
LINlinearNoisy, LINret, LINexp, D1MSN and D2MSN.

The LINlinear component governs the activation $a$ with a first order
leaky integrator differential equation:
\[
   \dot{a} = {1 \over \tau}(a_{in}-a)
\]
where $\tau$ is the time constant for the neural activation and
$a_{in}$ is the input to the neural element. $a_{in}$ is defined by an
activation input and a shunting inhibition input according to:
\[
   a_{in} = A(1-s_a)+0.01 R_N
\]
Here, $A$ is the activation input and $s_a$ is the shunting inhibition
state variable whose value is related to the shunting input, $S$ by
\[
   s_a = \begin{cases}
      S & S\leq 1 \\
      1 & S > 1
   \end{cases}
\]
$R_N$ is a random number drawn from a
standard normal distribution ($\sigma$=1, $\mu$=0) and introduces noise
to the activation of the neural element.

@@

LINlinearNoisy is identical to LINlinear with the single exception
that the level of noise is increased. This means that the equation for
$a_{in}$ must be rewritten:
\[
   a_{in} = A(1-s_a)+0.2 R_N
\]
The LINret component used for the retinal populations is again similar
to the LINlinear component, but with no intrinsic noise and no
shunting inhibitory input. It has a neural input which is identical to
the activation input $A$:
\[
   a_{in} = A
\]
The LINexp component is a leaky integrator with an exponential
transfer function. It shares the same differential equation with
LINlinear, but has a different input equation and a different output
transfer function. It has the following equation for the neural
element input $a_{in}$:
\[
   a_{in} = [A+N(a-V_{r}^{-})] (1-S) + 0.01 R_N
\]
where $A$ is the activation input and $N$ is an input which is
modulated by $V_{r}^{-}$, a reversal potential, and $a$, the current
activation of the element. These inputs are summed and then reduced by
a factor which is dependent on $S$, the shunting input. As in
LINlinear, $R_N$ introduces normally distributed noise to the element.

@@

@@

\subsubsection{Population activity}

Each population of 2500 neural elements is arranged in a 50 by 50
grid, with positions on the grid representing a retinotopic
mapping. Locations on the grid specify radial and azimuthal angles r
and $\phi$ for the location of activity on the retina relative to the
fovea. r and $\phi$ can be converted into rotations about the $x$ and
$y$ Cartesian axes ($\theta_x$ and $\theta_y$). The result of a
positive rotation about the $x$ axis in a right-handed Cartesian
coordinate system results in an upward movement of the fovea's view
of the environment. Note that a positive rotation about the $y$ axis
results in a \emph{leftward} movement.

Note that the mapping encompases the entire visual field. The value of
$\phi$ is allowed to vary from 0 to 360\degrees along its axis.
Effectively, the two contralateral colliculi are incorporated into a
single, square map, avoiding the need to carry out `colliculus
gluing'~\cite{tabareau_geometry_2007}.

The magnification factor, $M_f$, gives the relationship between the
radial angle r and the retinal neural density. It is given by:
\[
   M_f = {W_{nfs} \over E_2 ln ({W_{fov} \over 2 E_2} + 1)}
\]
where $W_{nfs}$ is the width of the retinotopic neural fields (50),
$W_{fov}$ is the eye's field of view, which is set to 61 degrees, a
reduction from the biophysically accurate 150 degrees due to the small
number of neurons in the retinotopic neural field. $E_2$ is the
eccentricity (in degrees) at which the retinal neural density has
halved compared with the foveal region.

@@

Figure \ref{fig:mapping} shows the result of the mapping for a view of two
cross-shaped luminances. One cross illuminates the fovea, which
results in a large comb-shape of activity. The more peripheral cross
produces an indistinct object centered at a larger value of r.

@@

Briefly, the model consists of input from the World population
producing activity in an `express' pathway to superior colliculus
and simultaneously in cortex, represented here by the FEF
population. The express pathway causes short latency activity in the
superficial superior colliculus, which directly innervates the deeper
layers of the superior colliculus (SC\_deep). Activity in FEF
generates firing in a thalamo-cortico-basal ganglia loop. The output
of the basal ganglia is the substantia nigra pars reticulata (SNr)
which tonically inhibits SC\_deep. If a location of activity in FEF is
able to dominate selection in the basal ganglia circuit, the
corresponding location in SNr will dis-inhibit and activity will build
up in SC\_deep encoding the saccade end point.

Connections shown in red are one to one connections; dark blue
connections indicate a connectivity pattern which `fans out' with a 2-D
Gaussian kernel; lighter blue connections from STN to SNr and GPe are
diffuse, all to all connections and connections in green are one to one
connections that decay towards the fovea so that foveal activity in
FEF does not swamp the basal ganglia which would prevent peripheral
luminances from being selected.

Note that SC\_deep contains two recurrent connections; one is
excitatory, with a Gaussian kernel mapping and the other implements
tecto-tectal inhibition, which increases the inhibition between
activity in opposite hemispheres of the field of view (refs). The
tecto-tectal inhibitory connection is \emph{not} present in the \ccg
model.

@@

Neurons in the deep layers of the superior colliculus called long lead
burst neurons innervate excitatory burst neurons in the reticular
formation (ref). In this model, we implement a network based
on \cite{gancarz_neural_1998}.

@@

% Section - description of the integration
\subsection{Integrating the models and closing the loop}

@@

% trajectories, neuron activations (esp. brainstem). latency vs
% dopamine, latency vs gap.
%
% The importance of an even sized hill of activity in SC_deep. The difficulties of achieving this.

@@

SJ, AB and AC implemented existing parts of the model in SpineML. AB
developed the saccade generator brainstem model. SJ performed the
technical and scientific integration of the biomechanical eye.
DS, CP and KM developed the biomechanical eye model. SJ wrote the 
manuscript. KG conceived the experiment. % FIXME: This needs correcting/developing.

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/mapping.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:mapping} Figure \arabic{figure}.}
{ \textbf{fig:mapping} Representative mapping from eye's frame of reference in cartesian
coordinates to retinotopic coordinates. (a) The mapping of luminances
in the eye's frame of reference. The world input is pre-defined by a
JSON configuration file. luminance position, size and shape can be
defined in this file, along with the times at which luminances appear
and disappear. The worldDataMaker.cpp code computes the locations of
the luminances in the eye's frame of reference, given its rotational
state. Here, there are two cross shaped luminances, one at the
fixation point (0,0) and one at a peripheral position (4,-10). (b) The
locations of the luminances in the eye's frame of reference are then
converted into retinotopic coordinates, with centrally located
luminances being represented at low values of $r$ and more peripheral
luminances having higher values of $r$. $phi$ encodes rotational
angle: 12.5 is up, [etc etc]. The output of the World component is fed
into FEF\_add\_noise and into the retinal neuron populations. (c) The
FEF\_add\_noise populations adds a level of noise to the signal
representing processing of the signal in visual cortex. (d) The
activity in FEF is the input to the basal ganglia and one input to
superior collicus.}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=\textwidth]{./figures/weightmaps.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:weightmaps} Figure \arabic{figure}.}
{ \textbf{fig:weightmaps} Weight maps}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/outmany.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:outmany} Figure \arabic{figure}.}
{ \textbf{fig:outmany} Representative single saccades.}
\end{figure}

>>>>

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{James {et~al.}}
\def\Authors{Sebastian James\,$^{1,2,*}$, Chris Papapavlou\,$^5$, Alexander Blenkinsop\,$^{1,2}$, \\
  Alexander Cope\,$^3$,  \\
  Sean Anderson\,$^{2,4}$, Konstantinos Moustakas\,$^5$, Kevin Gurney\,$^{1,2}$}
% Affiliations should be keyed to the author's name with superscript
% numbers and be listed as follows: Laboratory, Institute, Department,
% Organization, City, State abbreviation (USA, Canada, Australia), and
% Country (without detailed address information such as city zip codes
% or street names).
%
% If one of the authors has a change of address, list the new address
% below the correspondence details using a superscript symbol and use
% the same symbol to indicate the author in the author list.
\def\Address{\\
$^{1}$Adaptive Behaviour Research Group, Department of Psychology,
  The University of Sheffield, Sheffield, UK \\
$^{2}$Insigneo Institute for in-silico Medicine,
  The University of Sheffield, Sheffield, UK \\
$^{3}$Department of Computer Science,
  The University of Sheffield, Sheffield, UK \\
$^{4}$Department of Automatic Control Systems Engineering,
  The University of Sheffield, Sheffield, UK \\
$^{5}$Department of Computer Science,
  The University of Patras, Patras, Greece \\
}
% The Corresponding Author should be marked with an asterisk. Provide
% the exact contact address (this time including street name and city
% zip code) and email of the corresponding author
\def\corrAuthor{Kevin Gurney}
\def\corrAddress{Department of Psychology, The University of Sheffield,
  Western Bank, Sheffield, S10 2TP, UK}
\def\corrEmail{k.gurney@sheffield.ac.uk}

@@

In addition to the brain model components, all of which are
code-generated using \stob~as described above, two hand-written
components are integrated into the model: The biomechanical eye model
and a sensory input component. The sensory input component takes the
eye's rotational state and the state of the experimental luminances
and projects a retinotopic activity map into the brain model. Both of
these BRAHMS components were hand-written in C++. To incorporate these
components into the SpineML model, a model-specific modification was
applied in \stob~(\mycite{cope_spineml_2_brahms_2015}) making use of
a \stob~feature designed for this purpose (The external.xsl file).

Figure \ref{fig:model_framework} shows the workflow, in which the
model specification files (blue box - a combination of SpineML files
and C++ code), are processed (green box) into a BRAHMS system (red
box).

@@

With the exceptions of the World and FEF\_add\_noise populations, each
neural element represents an activation; the activation is governed by
a first order differential equation specified in the SpineML
component. In the brain model, there are six different components in
use: LINlinear; LINret; LINexp; D1MSN and D2MSN.

The LINlinear component governs the activation $a$ with a first order
leaky integrator differential equation:
\[
   \dot{a} = {1 \over \tau}(a_{in}-a)
\]
where $\tau$ is the time constant for the neural activation and
$a_{in}$ is the input to the neural element. $a_{in}$ is defined by an
activation input and a shunting inhibition input according to:
\[
   a_{in} = A(1-s_a)+\alpha R_N
\]
Here, $A$ is the activation input and $s_a$ is the shunting inhibition
state variable whose value is related to the shunting input, $S$ by
\[
   s_a = \begin{cases}
      S & S\leq 1 \\
      1 & S > 1
   \end{cases}
\]
$R_N$ is a random number drawn from a standard normal distribution
($\sigma$=1, $\mu$=0) and introduces noise to the activation of the
neural element, with the parameter $\alpha$ controlling the noise
amplitude.

@@

The LINret component used for the retinal populations is again similar
to the LINlinear component, but with no intrinsic noise and no
shunting inhibitory input. It has a neural input which is identical to
the activation input $A$:
\[
   a_{in} = A
\]
The LINexp component is a leaky integrator with an exponential
transfer function. It shares the same differential equation with
LINlinear, but has a different input equation and a different output
transfer function. It has the following equation for the neural
element input $a_{in}$:
\[
   a_{in} = [A+N(a-V_{r}^{-})] (1-S) + 0.01 R_N
\]
where $A$ is the activation input and $N$ is an input which is
modulated by $V_{r}^{-}$, a reversal potential, and $a$, the current
activation of the element. These inputs are summed and then reduced by
a factor which is dependent on $S$, the shunting input. As in
LINlinear, $R_N$ introduces normally distributed noise to the element.

@@

The D1MSN and D2MSN components are both leaky integrators, similar to
LINlinear. They differ in that they have no shunting inhibition and a
dopamine parameter dependent modulation of the input activation, so
that their equations for $a_{in}$ are:
\[
   a_{in}^{D1} = (0.2 + d)A + 0.01 R_N
\]
for D1MSN, and
\[
   a_{in}^{D2} = (1 - d)A + 0.01 R_N
\]
for D2MSN, where $d$ is a dopamine parameter. Increasing dopamine from
0 to 1 enhances the activation in the D1 model neurons, whereas it
decreases the activation of the D2 model neurons, in line with
experimental observations~\cite{refs}. Note that the equation for
$a_{in}^{D1}$ differs from that used in the \ccg~model, for which the
cortico-striatal weights are multiplied by $(1+d)$ rather than $(0.2+d)$

The equations given above apply to each element in the population
whose behaviour is defined by the component. The value of the
activation $A$ (and where relevant the shunting input, $S$, also) is
determined by summing the weighted inputs to the population:
\[
A = \sum_{i}w_i^{act} x_i^{act}
\]
\[
S = \sum_{i}w_i^{sh} x_i^{sh}
\]

@@

\subsubsection{Population activity and retinotopic mapping}

Each population of 2500 neural elements is arranged in a 50 by 50
grid, with positions on the grid representing a retinotopic
mapping. Locations on the grid specify radial and azimuthal angles $r$
and $\phi$ for the location of activity on the retina relative to the
fovea. $r$ and $\phi$ can be converted into rotations about the $x$ and
$y$ Cartesian axes ($\theta_x$ and $\theta_y$). The result of a
positive rotation about the $x$ axis in a right-handed Cartesian
coordinate system results in an upward movement of the fovea's view
of the environment. Note that a positive rotation about the $y$ axis
results in a \emph{leftward} movement of the eye's focal point, with
respect to the world.

Note that the mapping encompases the entire visual field. The value of
$\phi$ is allowed to vary from 0$\deg$ to 360$\deg$ along its axis.
Effectively, the two contralateral colliculi are incorporated into a
single, square map, avoiding the need to carry out `colliculus
gluing'~\cite{tabareau_geometry_2007}.

The magnification factor, $M_f$, gives the relationship between the
radial angle $r$ and the retinal neural density. It is given by:
\[
   M_f = {W_{nfs} \over E_2 ln ({W_{fov} \over 2 E_2} + 1)}
\]
where $W_{nfs}$ is the width of the retinotopic neural fields (50),
$W_{fov}$ is the eye's field of view, which is set to 61 degrees, a
reduction from the biophysically accurate 150 degrees due to the small
number of neurons in the retinotopic neural field. $E_2$ is the
eccentricity (in degrees) at which the retinal neural density has
halved compared with the foveal region.

@@

Figure \ref{fig:mapping} shows the result of the mapping for a view of
two cross-shaped luminances. One cross illuminates the fovea, which
results in a large comb-shape of activity. The more peripheral cross
produces (in FEF) an indistinct object centered at a larger value of
r.

@@

Briefly, the model consists of input from the World population (see
Fig.~\ref{fig:brain_model}, green population box) producing activity
in an `express' pathway to superior colliculus (purple) and
simultaneously in cortex, represented here by the FEF population (grey
boxes in Fig.~\ref{fig:brain_model}). The express pathway causes short
latency activity in the superficial superior colliculus, which
directly innervates the deeper layers of the superior colliculus
(SC\_deep). Activity in FEF generates firing in a
thalamo-cortico-basal ganglia loop. The output of the basal ganglia is
the substantia nigra pars reticulata (SNr) which tonically inhibits
SC\_deep. If a location of activity in FEF is able to dominate
selection in the basal ganglia circuit, the corresponding location in
SNr will dis-inhibit and activity will build up in SC\_deep encoding
the saccade end point.

Connections shown in red are one to one connections; dark blue
projections indicate a connectivity pattern which `fans out' with a
2-D Gaussian kernel; lighter blue connections from STN to SNr and GPe
are diffuse, all-to-all connections and projections coloured green are
one-to-one connections that decay towards the fovea so that foveal
activity in FEF does not swamp the basal ganglia which would prevent
peripheral luminances from ever being selected.

Note that SC\_deep contains two recurrent connections; one is
excitatory, with a Gaussian kernel mapping and the other implements
tecto-tectal inhibition, which increases the inhibition between
activity in opposite hemispheres of the field of view (refs). The
tecto-tectal inhibitory connection is \emph{not} present in
the \ccg~model.

@@

In this model, we implement a saccadic burst generator (SBG) based
on \cite{gancarz_neural_1998}. The SBG network for two of the model's
six channels is shown in Fig.~\ref{fig:sbg}. Activity from the output
layer of superior colliculus (SC\_avg) is fed into each channel, which
sums the activity it receives and processes it in populations each of
a single neural element representing all the neurons in that
population.

Neurons in the deep
layers of the superior colliculus called long lead burst neurons
innervate excitatory burst neurons in the reticular formation (REF,
and check if LLBNs are really in SC).

Alex B to write this section?

Note that inhibition from IBN populations is fed back - or is this
detail for the `integration' subsection?

@@

% Section - description of the integration. scientific and
% technical. Already
\subsection{Integrating the models and closing the loop}

The \ccg~model closed its loop by passing the centroid of activity in
SC\_deep (once it had surpassed a threshold) back to the code that
controlled the world, which would then use this location to
instantaneously change the model's view of the world. In our extended
model, it was necessary to connect the output of the brain model back
to its input via the saccadic burst generator model and the
biomechanical eye. The resulting state of the eye, rather than the
centroid of the superior colliculus, was used to compute the input to
the brain, given the luminances visible in the world.

% Brain to SBG, seeing as that's how I explained it above.
A number of studies have considered the form of the connection between
the deeper layers of the superior colliculus and the saccadic burst
generator~\cite{van_gisbergen_experimental_1985,ottes_visuomotor_1986,waitzman_superior_1991,groh_converting_2001,arai_model_2004,goossens_dynamic_2006,tabareau_geometry_2007,van_opstal_linear_2008,goossens_optimal_2012},
which has become known as the spatial temporal transform (STT).  The
spatial part of the STT is thought to be implemented by a
weight-mapping~\cite{tabareau_geometry_2007,arai_model_2004} and we
follow this idea.

% Words along the lines of:
Arai and co-workers trained their neural network model to discover the
weight map~\cite{arai_model_2004}.

% Then...
Tabareau and co-workers wrote down the theoretical form of the weight
map and found it matches well to the results of Arai et
al.~\cite{tabareau_geometry_2007}.

The approach of Arai~et.~al. was
not feasible with the present model due to the length of time required
to run the model, its stochasticity and the increased size of the maps
here compared with those used by Arai~et.~al.

The saccadic burst generator model was originally conceived with the
assumption of a step input~\cite{gancarz_neural_1998}.

% SBG to worldDataMaker
The output signals from the six channels of the SBG were connected to
the six motoneuron inputs of the biomechanical eye. The signal was
normalised; a value of 1 meaning that all the motoneurons in the
output population were firing at their maximum rate and the force
exerted by the relevant extraocular muscle was maximal. Channels
innervated extraocular muscles as follows: Up: superior rectus; Down:
inferior rectus; Right: medial rectus; Left: lateral rectus; Z+:
superior oblique; Z-: inferior oblique. Because the medial rectus
induces a rightward rotation of the eye, our single virtual eye is
a \emph{left} eye. The OpenSim implementation of the biomechanical eye
was `wrapped' (in the software sense) in a BRAHMS component. This made
it possible to integrate the OpenSim model into the BRAHMS
framework. The wrapper ensured that the input and output signals were
correctly transferred and, importantly, handled the disparity in the
solver timesteps used in the OpenSim model (25~ms) and the neural
model (1~ms). This was achieved by having the BRAHMS wrapper create a
separate thread to run the OpenSim model. The BRAHMS wrapper component
was called on each 1 ms timestep, receiving the instantaneous
activations from the motoneurons in the SBG. These activations, and
the current simulation time, were written into a shared memory area,
accessible by the OpenSim thread. Running independently, the OpenSim
thread would update its inputs (using the most recent values in the
shared memory area) whenever the simulation time had increased by 25
ms. It would then recompute its outputs (the rotational state of the
eye) and write these into the same, shared memory. The BRAHMS wrapper
would update its outputs whenever they were changed in the shared
memory by the OpenSim thread. A direct connection of the six outputs
of the BRAHMS eye model component to the six inputs of the
worldDataMaker BRAHMS component was specified in
the \stob~external.xsl file.

% worldDataMaker to brain, but Re-work:
The eye model outputs its rotational state at each
timestep. The rotational state is used to compute the view of the
world in the eye's frame of reference. To simplify
the calculation, the luminances exist on a spherical surface at the
centre of which is the eye. A hand-coded BRAHMS component called
worldDataMaker computes the projection of the luminances into the
eye's frame of reference and then converts this representation into a
retinotopic map to pass into the brain model. The input to the brain
model is thus able to change continuously, on every timestep, rather
than in a step-wise fashion when a saccade occurs, as in the \ccg~model.

In the worldDataMaker BRAHMS component, the rotational state of the
eye was used to construct Euler rotation matrices which transformed
between the world's frame of reference and the eye's frame of
reference. The worldDataMaker component received a specification of
the world luminances in a JSON file called luminances.json at the
start of each simulation. luminances.json specified the position,
shape, size, luminance, appearance time and disappearance time of an
arbitrary number of luminances. With this information, the
instantaneous rotational state of the eye and the parameters of the
retinotopic transform, it was able to compute the instantaneous input
to the brain model.

@@

% trajectories, neuron activations (esp. brainstem). latency vs
% dopamine, latency vs gap.
%
% The importance of an even sized hill of activity in SC_deep. The
% difficulties of achieving this.

\subsection{Weight maps (here?)}

\subsection{Single saccades}

@@

SJ, AB and AC implemented existing parts of the model in SpineML. AB
developed the saccade generator brainstem model. SJ performed the
technical and scientific integration of the biomechanical eye.  CP and
KM developed the biomechanical eye model. SJ wrote the manuscript; SA,
AB, KG and KM contributed to the manuscript. KG conceived the
project.

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.9\textwidth]{./figures/mapping.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:mapping} Figure \arabic{figure}.}
{ \textbf{fig:mapping} Representative mapping from eye's frame of
reference in cartesian coordinates to retinotopic coordinates. (a) The
mapping of luminances in the eye's frame of reference. The world input
is pre-defined by a JSON configuration file. Luminance position, size
and shape can be defined in this file, along with the times at which
luminances appear and disappear. The worldDataMaker.cpp code computes
the locations of the luminances in the eye's frame of reference, given
its rotational state. It also computes a 2D gaussian convolution of
the luminances. Here, there are two cross shaped luminances spanning
10$\deg$, one of value 0.8 at the fixation point (0,0) and one of
value 0.5 at a peripheral position (0,-12$\deg$). (b) The locations of
the luminances in the eye's frame of reference are then converted into
retinotopic coordinates, with centrally located luminances being
represented at low values of $r$ and more peripheral luminances having
higher values of $r$. $\phi$ encodes rotational angle: 1 and 50 encode
upward movement; 13 is left; 25 is down; 37 is right. The output of
the World component is fed into FEF\_add\_noise and into the retinal
neuron populations. The colour map makes it possible to distinguish
between the two crosses. (c) The FEF\_add\_noise populations adds a level
of noise to the signal representing processing of the signal in visual
cortex. (d) A Gaussian projection from FEF\_add\_noise to FEF further
blurs the activity in FEF. FEF is the input to the basal ganglia and
one input to superior collicus.}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=\textwidth]{./figures/weightmaps.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:weightmaps} Figure \arabic{figure}.}
{ \textbf{fig:weightmaps} Weight maps for the connections between the
output layer of superior colliculus and the six long lead burst
neurons of the saccadic burst generator model. Each map increases
exponentially with increasing $r$, multiplied by cosine($\phi$) about
its `active' axis. \textbf{FIXME: Left \& Right are wrong way round}}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.8\textwidth]{./figures/outmany.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:outmany} Figure \arabic{figure}.}
{ \textbf{fig:outmany} Representative single saccades. a) Trajectories
from 9 saccades to a single target at 9 different locations. In each
case, a fixation cross luminance of magnitude 0.2 was displayed at
(0,0), the start position of the eye, until time 0.4~s. The target
luminance, magnitude 0.3 was illuminated at time 0.4~s. Trajectory
shape is dependent on the target position, and there is a variable
amount of error in the end-points achieved by the model. Colour is
used in this diagram as an aid to distinguishing different saccades
and their targets; for a given saccade, the target location is given
by the cross of the same colour closest to the end of the
trajectory. b) The three rotational components of the `blue' saccade,
to target location (-7,-7). c) The three rotational components of the
`red' saccade, to target location (0,-10).}
\end{figure}
